Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-10 paper.tex
Add a link to Table 1 in the text

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - Blue Obelisk Open Source Software projects listed in the text}
    \par \mbox{}
    \par
    \mbox{
     \begin{tabular}{|c|c|c|}
       \hline \textbf{Name} & \textbf{Website}  \\ \hline
        \multicolumn{2}{|c|}{\textbf{CML Tools}} \\ \hline
        \textbf{CMLXOM} & https://bitbucket.org/wwmm/cmlxom/ \\ \hline
        \textbf{JUMBO} & http://sourceforge.net/projects/cml/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Cheminformatics Toolkits}} \\ \hline
        \textbf{Chemistry Development Kit (CDK)} & http://cdk.sf.net \\ \hline
        \textbf{Cinfony} & http://cinfony.googlecode.com \\ \hline
        \textbf{Indigo} & http://ggasoftware.com/opensource/indigo \\ \hline
        \textbf{JOELib} & http://sf.net/projects/joelib \\ \hline
        \textbf{Open Babel} & http://openbabel.org \\ \hline
        \textbf{RDKit} & http://rdkit.org \\ \hline
        \multicolumn{2}{|c|}{\textbf{Web Applications}} \\ \hline
        \textbf{ChemDoodle Web Components} & http://web.chemdoodle.com \\ \hline
        \textbf{gChem} & http://metamolecular.com/gchem/ \\ \hline
        \textbf{Jmol} & http://jmol.org \\ \hline
        \multicolumn{2}{|c|}{\textbf{Integration}} \\ \hline
        \textbf{Bioclipse} & http://www.bioclipse.net \\ \hline
        \textbf{CDK-Taverna} & http://cdktaverna.wordpress.com \\ \hline
        \textbf{Lensfield2} & https://bitbucket.org/sea36/lensfield2/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Interconversion}} \\ \hline
        \textbf{CIFXOM} \cite{DayEtAl2011} & https://bitbucket.org/wwmm/cifxom/  \\ \hline
        \textbf{JUMBO-Converters} & https://bitbucket.org/wwmm/jumbo-converters/ \\ \hline
        \textbf{OPSIN} & http://opsin.ch.cam.ac.uk \\ \hline
        \textbf{OSRA} & http://osra.sf.net \\ \hline
        \multicolumn{2}{|c|}{\textbf{Structure Databases}} \\ \hline
        \textbf{Bingo}  & http://ggasoftware.com/opensource/bingo \\ \hline
        \textbf{Chempound (Chem\#)} & https://bitbucket.org/chempound \\ \hline
        \textbf{MyChem}  & http://mychem.sf.net \\ \hline
        \textbf{OrChem} & http://orchem.sf.net \\ \hline
        \textbf{pgchem}  & http://pgfoundry.org/projects/pgchem/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Text mining}} \\ \hline
        \textbf{ChemicalTagger} \cite{HawizyEtAl2011} & http://chemicaltagger.ch.cam.ac.uk/ \\ \hline
        \textbf{OSCAR4} & https://bitbucket.org/wwmm/oscar4/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Computational Chemistry}} \\ \hline
        \textbf{Avogadro} & http://avogadro.openmolecules.net \\ \hline
        \textbf{cclib}  & http://cclib.sf.net \\ \hline
        \textbf{GaussSum}  & http://gausssum.sf.net \\ \hline
        \textbf{QMForge}  & http://qmforge.sf.net \\ \hline
        \multicolumn{2}{|c|}{\textbf{Computational Drug Design}} \\ \hline
        \textbf{Confab}~\cite{Confab} & http://confab.googlecode.com \\ \hline
        \textbf{Pharao} & http://silicos.be/download \\ \hline
        \textbf{Piramid} & http://silicos.be/download \\ \hline
        \textbf{Sieve} & http://silicos.be/download \\ \hline
        \textbf{Stripper} & http://silicos.be/download \\ \hline
        \multicolumn{2}{|c|}{\textbf{Other Applications}} \\ \hline
        \textbf{AMBIT2}  & http://ambit.sf.net \\ \hline
        \textbf{Brunn}  & http://brunn.sf.net \\ \hline
        \textbf{XtalOpt}  & http://xtalopt.openmolecules.net \\ \hline
        \hline
       \end{tabular}
      }

>>>>

The development of Open Source software has been one of the most
successful of the Blue Obelisk's activities. The following sections
describe recent work in this area, and Table 1
provides an overview of the projects
discussed and where to find them online.

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - Blue Obelisk Open Source Software projects discussed in the text}
    \par \mbox{}
    \par
    \mbox{
     \begin{tabular}{|c|c|c|}
       \hline \textbf{Name} & \textbf{Website}  \\ \hline
        \multicolumn{2}{|c|}{\textbf{CML Tools}} \\ \hline
        \textbf{CMLXOM} & https://bitbucket.org/wwmm/cmlxom/ \\ \hline
        \textbf{JUMBO} & http://sourceforge.net/projects/cml/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Cheminformatics Toolkits}} \\ \hline
        \textbf{Chemistry Development Kit (CDK)} & http://cdk.sf.net \\ \hline
        \textbf{Cinfony} & http://cinfony.googlecode.com \\ \hline
        \textbf{Indigo} & http://ggasoftware.com/opensource/indigo \\ \hline
        \textbf{JOELib} & http://sf.net/projects/joelib \\ \hline
        \textbf{Open Babel} & http://openbabel.org \\ \hline
        \textbf{RDKit} & http://rdkit.org \\ \hline
        \multicolumn{2}{|c|}{\textbf{Web Applications}} \\ \hline
        \textbf{ChemDoodle Web Components} & http://web.chemdoodle.com \\ \hline
        \textbf{gChem} & http://metamolecular.com/gchem/ \\ \hline
        \textbf{Jmol} & http://jmol.org \\ \hline
        \multicolumn{2}{|c|}{\textbf{Integration}} \\ \hline
        \textbf{Bioclipse} & http://www.bioclipse.net \\ \hline
        \textbf{CDK-Taverna} & http://cdktaverna.wordpress.com \\ \hline
        \textbf{Lensfield2} & https://bitbucket.org/sea36/lensfield2/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Interconversion}} \\ \hline
        \textbf{CIFXOM} \cite{DayEtAl2011} & https://bitbucket.org/wwmm/cifxom/  \\ \hline
        \textbf{JUMBO-Converters} & https://bitbucket.org/wwmm/jumbo-converters/ \\ \hline
        \textbf{OPSIN} & http://opsin.ch.cam.ac.uk \\ \hline
        \textbf{OSRA} & http://osra.sf.net \\ \hline
        \multicolumn{2}{|c|}{\textbf{Structure Databases}} \\ \hline
        \textbf{Bingo}  & http://ggasoftware.com/opensource/bingo \\ \hline
        \textbf{Chempound (Chem\#)} & https://bitbucket.org/chempound \\ \hline
        \textbf{MyChem}  & http://mychem.sf.net \\ \hline
        \textbf{OrChem} & http://orchem.sf.net \\ \hline
        \textbf{pgchem}  & http://pgfoundry.org/projects/pgchem/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Text mining}} \\ \hline
        \textbf{ChemicalTagger} \cite{HawizyEtAl2011} & http://chemicaltagger.ch.cam.ac.uk/ \\ \hline
        \textbf{OSCAR4} & https://bitbucket.org/wwmm/oscar4/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Computational Chemistry}} \\ \hline
        \textbf{Avogadro} & http://avogadro.openmolecules.net \\ \hline
        \textbf{cclib}  & http://cclib.sf.net \\ \hline
        \textbf{GaussSum}  & http://gausssum.sf.net \\ \hline
        \textbf{QMForge}  & http://qmforge.sf.net \\ \hline
        \multicolumn{2}{|c|}{\textbf{Computational Drug Design}} \\ \hline
        \textbf{Confab}~\cite{Confab} & http://confab.googlecode.com \\ \hline
        \textbf{Pharao} & http://silicos.be/download \\ \hline
        \textbf{Piramid} & http://silicos.be/download \\ \hline
        \textbf{Sieve} & http://silicos.be/download \\ \hline
        \textbf{Stripper} & http://silicos.be/download \\ \hline
        \multicolumn{2}{|c|}{\textbf{Other Applications}} \\ \hline
        \textbf{AMBIT2}  & http://ambit.sf.net \\ \hline
        \textbf{Brunn}  & http://brunn.sf.net \\ \hline
        \textbf{XtalOpt}  & http://xtalopt.openmolecules.net \\ \hline
        \hline
       \end{tabular}
      }
